Object-Oriented Internet - Azure Interoperability

### 2020-12-02 Latex/Manuscript.tex

      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Internet of Things. This research aims at working out a new generic architecture and deployment scenario applicable to this integration. The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets mobility. Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment. The discussion addressing the generic architecture concludes that the embedded gateway archetype best suits all requirements. To promote separation of concerns and reusability, the implementation of the embedded gateway archetype has been implemented as a composable part of an existing OPC UA PubSub framework.

@@

Today both obstacles can be overcome, and as examples, we have bank account remote control and voice over IP in daily use. The first application must be fine-tuned in the context of data security, and the second is very sensitive in regard to time constraints. Similar approaches could be applied to adopt the well known in process control industry concepts:

@@

If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship could relax the problems encountered while the interactive approach is applied. In this case, the sessionless publisher-subscriber communication relationship is a typical pattern to implement the abstract reactive interoperability paradigm. The sessionless relationship is a message distribution scenario where senders of messages, called publishers, do not send them directly to specific receivers, called subscribers, but instead, categorize the published messages into topics without knowledge about which subscribers if any, there may be. Similarly, subscribers express interest in one or more topics and only receive messages that are of interest, without knowledge about which publishers, if any, there are. In this scenario, the publishers and subscribers are loosely coupled i.e they are decoupled in time, space and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.

@@

This article addresses further research on the integration of the CPS in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT). The new architecture is proposed for integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end. To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected. The proposals are backed by proof of concept reference implementations. Prototyping addresses Microsoft Azure Cloud as an example. The prototyping outcome has been just published on GitHub as the open-source (MIT licensed) [TODO: Add reference?]. The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.

@@

If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship\cite{mpostol2020} could alleviate the challenges posed by the interactive approach. The real-time multi-vendor environment makes communication standardization especially important. To support this environment, OPC Unified Architecture \cite{RefWorks:doc:5ac86c98e4b009947bbb874c} interoperability standard has been selected. As it was pointed out in the Sect. \ref*{subs.architecture} using OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} the aggregation of nodes by the network is loosely coupled, i.e. nodes can be added and removed from the network dynamically, and nodes may represent mobile data holding assets.

>>>>

      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Industrial Internet of Things. This research aims at working out a new generic architecture and deployment scenario applicable to this integration. The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets' mobility. Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment. The discussion addressing the generic architecture concludes that the embedded gateway archetype best suits all requirements. To promote separation of concerns and reusability, the proposed architecture of the embedded gateway archetype has been implemented as a composable part of an existing OPC UA PubSub framework.

@@

Today both obstacles can be overcome, and as examples, we have bank account remote control and voice over IP in daily use. The first application must be fine-tuned in the context of data security, and the second is very sensitive on time relationships. Similar approaches could be applied to adopt the well known in process control industry concepts:

@@

If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship could relax the problems encountered while the interactive approach is applied. In this case, the sessionless publisher-subscriber communication relationship is a typical pattern to implement the abstract reactive interoperability paradigm. The sessionless relationship is a message distribution scenario where senders of messages, called publishers, do not send them directly to specific receivers, called subscribers, but instead, categorize the published messages into topics without knowledge about which subscribers if any, there may be. Similarly, subscribers express interest in one or more topics and only receive messages that are of interest, without knowledge about which publishers, if any, there are. In this scenario, the publishers and subscribers are loosely coupled.i.e they are decoupled in time, space and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.

@@

This article addresses further research on the integration of the CPS in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT). The new architecture is proposed for integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end. To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected. The proposals are backed by proof of concept reference implementations. Prototyping addresses Microsoft Azure Cloud as an example. The prototyping outcome has been just published on GitHub as the open-source (MIT licensed). The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.

@@

If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship\cite{mpostol2020} could relax the problems encountered while the interactive approach is applied. The real-time multi-vendor environment makes communication standardization especially important. To support this environment, OPC Unified Architecture \cite{RefWorks:doc:5ac86c98e4b009947bbb874c} interoperability standard has been selected. As it was pointed out in the Sect. \ref*{subs.architecture} using OPC UA PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} the aggregation of nodes by the network is loosely coupled, i.e. nodes can be added and removed from the network dynamically, and nodes may represent mobile data holding assets.
